---
title: "Homework 4: Evaluating and Summarizing Data Analyses"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

#### Preface 

* **This homework is due Wednesday October 9, 2019 at 11:59 PM**. 
* When you have completed the assignment, knit the R Markdown, commit your changes and push to GitHub.
* If you do not include axis labels and plot titles, then points will be deducted.
* If you do not include prose/text after the sections titled "Add your answer here", then points will be deducted. 
* You are welcome and encouraged to discuss homework problems with others in order to better understand it, but the work you turn in must be your own. You must write your own code, data analyses, and communicate and explain the results in your own words and with your own visualizations. **All students turning in plagiarized solutions will be reported to Office of Academic Integrity, and will fail the assignment**.

# Motivation

One important skill in data science is to be able to **evaluate**
data analyses that you build, from your peers / colleagues, 
or data analyses that you see in the wild. In HW1 and HW4, 
you practiced the skills of critiquing and evaulating 
data analyses. 

A second important skill is being able to **summarize** the key 
ideas in a data analysis that either you built or one that is 
presented to you. 

In this homework assignment, you will practice both of these skills. 
Your goal is to evaluate and summarize a data analysis. But instead 
of working with a dataset and data analysis that you created, you 
will work with a set that someone else created. You will be 
randomly assigned someone else's dataset and analysis that they
created in HW3. 


# Problem 1

We have randomly assigned individuals using the `sample()` function 
in the code below. We only include first names here. 
Identify the person that you have been randomly assigned to, connect
with the individual (either in class, by email, or on slack) and ask 
them to share their `twitter_data_hw2.csv` file that they started with
in HW3 and their `711-hw3-assignment.Rmd` that they built in HW3. 
Save both of these into into **your** HW4 GitHub repo. This is 
the data and data analysis you will use for your HW4. 

```{r}
student_names <- c("Brian", "Erjia", "Eric", "Elizabeth", 
                   "Grant", "Haley", "Jennifer (Shiyao)",
                   "Jiyang", "Joe", "Jingning", "Linda", 
                   "Kate (Yueyi)", "Runzhe", "Yifan", "Zebin")

set.seed(123)
student_names <- student_names[sample(seq_along(student_names))]

set.seed(111)
data.frame("for_HW4" = student_names, 
           "use_this_data_from_HW3" = student_names[sample(seq_along(student_names))])
```

Identify the person that you have been randomly assigned to and 
get access to 

1. the `twitter_data_hw2.csv` file that they used in HW3
2. their data analysis (e.g. the `.Rmd`) that they built in HW3

Read the data analysis closely that they built (the `.Rmd`) and 
make sure you can reproduce their analysis results by kniting 
the RMarkdown document. Then, load the data into R using the 
`readr` package. 

```{r}
## add your code here

```


# Problem 2

Relfect on the analysis and answer the following questions: 

1. In terms of data storytelling and narrative, what is the 
central argument to this data analysis? 
2. What aspects of the analysis are included that support the 
story? Why do you believe these support the story? 
3. Are there any trust building elements? Why or why not? 
4. Do you believe the results of the analysis? Why or why not? 
5. What are some ways that the data and/or results could be 
misinterpreted? 

#### Add your answer here



# Problem 3 

Identify who was the audience that this analysis was built for
(this should be clearly stated in the analysis in HW3; if not, 
then make an educated guess). 

Describe the audience here: 

#### Add your answer here


Create a rubric (like you did in HW1
and a self evaluation in HW3) to evaluate the data analyst's 
analysis while keeping in mind who the audience was defined to 
be. As part of HW3, the analyst has provide a set of principles 
(HW3, Problem 2) that they prioritized when building the analysis.
They also provided a self-evaluation (HW3, Problem 4). 

Now, you have the opportunity to also evaluate this analysis. 
Using the data analysis principles and corresponding weights 
$w_i$ defined in HW3 by the data analyst, assign integer 
scores $S_i \in [0, 10]$ that represents how much the
given data analysis exhibits this principle where 0 is 
low and 10 is high. The scores can be similar (or different) 
than what was provided in HW3 by the data analyst.

For example if the principle is _reproduciblity_, give a score 
between 0 and 10 on how reproducible individual parts or the 
overall analysis (up to you) is where 0 is not reproducible
and 10 is reproducible. 

As a reminder, if there were only two principles, an example 
rubric might look like: 

```{r}
rubric <- data.frame(principle = rep(c("reproducbility", "exhaustive"),2),
                     weight = rep(c(0.1, 0.9), 2),
                     score_from_analyst_in_hw3 = c(10, 4, 2, 6), 
                     score_from_you =c(8, 9, 1, 4))
rubric
```


```{r}
## add your code here

```

Describe in words about why you gave the scores 
that you did. Do you think the analyst fairly 
evaluated themself? 

#### Add your answer here


Are there other principles that you believe should
have been included and/or removed? 

#### Add your answer here



# Problem 4

In this problem, you will practice creating 
data visualizations. 

## Problem 4.1 

Take one plot from HW3, reproduce it here: 

```{r}
## add your code here

```

Reflect on it and list four ways to improve it: 

#### Add your answer here


Next, implement those four changes to improve the plot. 

```{r}
## add your code here

```



## Problem 4.2

In this problem, you will practice the data analysis 
principle of _transparency_. Create one plot (or 
set of plots) that demonstrates _transparency_. You
cannot use a plot that was created by the data 
analyst in HW3 already.  

**Helpful hints**: as a reminder, the meaning of 
_transparent analyses_ are:  

> _Transparent analyses_ present an element or subset of elements
summarizing or visualizing data that are influential in 
explaining how the underlying data phenomena or data-generation 
process connects to any key output, results, or conclusions. While 
the totality of an analysis may be complex and involve a long sequence
of steps, transparent analyses extract one or a few elements from 
the analysis that summarize or visualize key pieces of evidence
in the data that explain the most "variation" or are most influential
to understanding the key results or conclusion. One aspect of being
transparent is showing the approximate mechanism by which the 
data inform the results or conclusion.


```{r}
## add your code here

```

Explain why you think this is a transparent plot. 

#### Add your answer here








# Problem 5
 
Another way to summarize the key ideas in an analysis is with words. 
Write the following:  

- a 15 word or less title for a press release
- a 500 word press release 
- a headline in 280 characters or less

For this problem, assume the audience is the general public. 

#### Write your press release title here


#### Write your press release here


#### Write your headline here 


